\section{Some extensions}
%///////////////////////////////////////



% /////////////////////////////////////////////////////////////////////////////
\subsection{Preference-based AF}



Several works generalizing Dung's framework to handle preferences over arguments have been proposed. 
% (Amgoud and Cayrol 1998, 2002; Amgoud and Vesic 2011, 2014; Cyras 2016; Silva, Sa ́, and Alcaˆntara 2020).



\begin{df}[Preference-based Argumentation Frameworks, PAFs]
    A \textit{preference-based argumentation framework} (PAF) is a triple $(Ar,\to,>)$ such that $(Ar,\to)$ is an AF and $>$ is a strict partial order on $Ar$ (i.e. an irreflexive, asymmetric and transitive relation), 
    called \textit{preference relation}.    
\end{df}



For any $a,b \in Ar$, 
$a > b$ means that $a$ is better than $b$ for the agent. 



The preference in a PAF $(Ar,\to,>)$ working as follows: 
classical argumentation semantics are used to obtain the extensions of the underlying AF $(Ar,\to)$, 
and then the preference relation $>$ is used to obtain a preference relation $\sqsupseteq$ over such extensions, 
so that the \textit{best extensions} w.r.t. $\sqsupseteq$ are eventually selected.


There have been different proposals to determine the best extensions, 
corresponding to different criteria to define $\sqsupseteq$ as explained in the following definition.

























% /////////////////////////////////////////////////////////////////////////////
\subsection{Value-based AF}


the motivation behind VAFs (value-based argumentation frameworks) is to offer an explanatory mechanism accounting for choices between distinct justifiable collections, 
$S$ and $T$, 
which are not collectively acceptable, 
i.e., $S$ and $T$ may be admissible under Dung's semantics, 
however, $S \cup T$ fails to be. 






%///////////////////////////////////////////////
\section{Probabilistic AF}

Recently, 
there are has been an increasing interest in modeling uncertainty in argumentation. 
% 
This has been carried out by combining probability theory with formal argumentation.
% 
The extension of Dung's abstract argumentation framework with probability theory is called \textit{probabilistic argumentation framework}.




In general a probabilistic argumentation framework consists of probabilistic arguments and probabilistic attacks  (Li, Oren, and Norman 2011; Fazzinga, Flesca, and Parisi 2015; Fazzinga, Flesca, and Furfaro 2019).
% 
As shown in \cite{Man.Bis2020},%\cite[p.214]{Man.Bis2020} 
however, 
an argumentation framework with probabilities on both arguments and attacks can be transformed into an equivalent one with certain attack relations (i.e. the probability of each attack is $1$).\footnote{
    The equivalent transformation between those two kinds of probabilistic AFs has linear complexity.
}
Hence, 
for the sake of brevity, 
in the section we only focus on probabilistic argumentation frameworks where only arguments are uncertain.



% \begin{df}[PrAFs \cite{Li.Ore.Nor2012}]
%     A \textit{probabilistic argumentation framework} (PrAF) is a tuple 
%     \[
%         (Ar,\to,p,p^\to)
%     \]
%     where $(Ar,\to)$ is an AF, 
%     $p$ and $p^\to$ are, respectively, 
%     functions assigning a non-zero probability value to each argument in $Ar$ and attack in $\to$, 
%     that is,
%     $p \colon Ar \to (0,1] \cap \mathbb{Q}$ and 
%     $p^\to\!: \to \; \to (0,1] \cap \mathbb{Q}$.
% \end{df}


\begin{df}[PrAFs]
    A \textit{probabilistic argumentation framework} (PrAF) is a tuple 
    \[
        PAF = (Ar,\to,p)
    \]
    where $(Ar,\to)$ is an argumentation framework and
    $p$ is a function assigning a non-zero probability value to each argument in $Ar$,
    that is,
    $p \colon Ar \to (0,1] \cap \mathbb{Q}$. 
\end{df}



\begin{remark}
    In some literature, 
    for instance ,

    
    the probability function is just $p \colon Ar \to (0,1]$.
\end{remark}



$p(a)$ is the probability that $a$ is actually present in the argumentation framework.




\vspace{1.5em}
\textit{justification perspective}:
$P(A)$ is treated as the probability that $a$ is a justified point and therefore should appear in the graph, 
and $1-P(A)$ is the probability that $A$ is not a justified point and so should not appear in the graph.

\vspace{1.5em}



Basically, 
the value assigned by $p$ to an argument $a$ represents the probability that $a$ actually occurs, 
% whereas the value assigned by $p^\to$ to a defeat $\langle a,b \rangle$ represents the conditional probability that $a$ defeats $b$ given that both $a$ and $b$ occur.
moreover, 
every attack $a \to b$ occurs with conditional prob- ability 1, 
that is, 
$a$ attacks $b$ whenever both $a$ and $b$ occur.



The meaning of a PrAF is given in terms of \textit{possible worlds}. 
Given a PrAF $\mathcal{PF}=(Ar,\to,p)$, 
a \textit{possible world} $w$ of $\mathcal{PF}$ is an AF $w=(Ar',\to')$ such that 
$w$ is the restriction of $(Ar,\to)$ to $Ar'$, 
that is, 
$Ar' \subseteq Ar$ and $\to' \;=\; \rightarrow \cap (Ar'\times Ar')$. 
% 
The set of all possible worlds of $\mathcal{PF}$ is denoted as $pw(\mathcal{PF})$.



\begin{df}[Subgraph]
\label{def: subgraph}
    For any given PrAF $\mathcal{PF}=(Ar,\to,p)$,     
    an AF $G = (Ar',\to')$ is a \textit{subgraph} $G$ of $\mathcal{PF}$,  $G \sqsubseteq \mathcal{PF}$ in symbol, 
    if $G$ is the restriction of the underlying AF $(Ar,\to)$ to $Ar'$, 
    i.e., 
    $Ar' \subseteq Ar$ and $\to' \;= (Ar'\times Ar')\; \cap \to$. 
    % 
    The set of all subgraphs of $\mathcal{PF}$ is denoted as $\mathsf{sub}(\mathcal{PF})$.
\end{df}


\begin{remark}
    \textit{possible world}  



    In literature, 
    the \textit{subgraph} in Def.~\ref{def: subgraph} is also called a \textit{full subgraph} \cite{Hun2013,Dod.Wol2014}.
    % 
    Obviously, 
    every $Ar' \subseteq Ar$ induces a unique (full) subgraph, 
    and the number of subgraphs is equals to $|\wp(Ar)|$.
\end{remark}



Thus, 
an argument $a \in Ar$ is viewed as a probabilistic event which is independent from the other events associated with other arguments 
$a \not=b \in Ar$.






use the probability distribution over arguments to generate a probability distribution over subgraphs of the original argument framework. 
% 
Using the subgraphs, 
we can then explore the notions of probability distributions over admissible sets, extensions, and inferences.





The intuition hereby is as follows: 
for $a \in Ar$, 
$p(a)$ is the probability that $a$ belongs to an arbitrary possible world (full subgraph) of $\mathcal{PF}$; 
while $1-p(a)$ is the probability that $a$ does not exist in an arbitrary possible world (full subgraph). 


(using the justification perspective \cite{Hun2012}, 
where $p(a)$ means the probability that $a$ is justified in appearing in the graph) 



\vspace{1.5em}


We can use the probability assigned to each argument to generate a probability distribution over the subgraphs. 
So each subgraph can be viewed as an ``interpretation'' of what the argument graph should be. 
If all the arguments have probability $1$, 
then the argument graph itself has probability $1$, 
and that is the only interpretation we should consider (using the constellations approach). 
But, if one or more arguments has a probability less than $1$, 
then there will be multiple ``interpretations''. 
% 
So for instance, 
if there is exactly one argument $a$ in the framework $G$ with probability less than $1$, 
then there are two “interpretations”, 
the first with $a$, 
and the second without $a$. 
% 
So using the justification perspective, 
with the constellations approach, 
we can treat the set of subgraphs of a $G$ as a \textit{sample space}, 
where one of the subgraphs is the ``true'' argument graph.


\vspace{1.5em}




\begin{df}
    The \textit{interpretation} for a PrAF $\mathcal{PF}=(Ar,\to,p)$ is  function 
    % {\color{purple} probability distribution function} 
    $I$ over the set $pw(\mathcal{PF})$. 
    % 
    Each $w \in pw(\mathcal{PF})$ is assigned by $I$ the probability 
    \[
        I(w) = \left( \prod_{a\in Arg(w)} p(a) \right) 
        \cdot
        \left( \prod_{a \in Ar \setminus Arg(w)} (1 - p(a)) \right)
    \]
    where $Arg(w)$ is the set of arguments in $w$.
\end{df}


Thus, 
the probability of a subgraph captures the degree of certainty that the subgraph contains exactly the arguments that are regarded as holding.


\begin{thm}[\cite{Li.Ore.Nor2011}, revised]
    Let $\mathcal{PF}=(Ar,\to,p)$ be a PrAF, 
    the function $I$ is a \textit{probability distribution} on the set $pw(\mathcal{PF})$, 
    i.e., 
    $I$ is a function such that 
    $\sum_{w \in pw(\mathcal{PF})} I(w) = 1$.
\end{thm}
\begin{proof}
    By induction on the size of $Ar$, 
    see the proof of Proposition 3 in \cite[p.~60]{Hun2013} for details.
\end{proof}




\begin{example}
    Considering following PrAF 
    \[G \qquad 
    \begin{tikzcd}
        a_1/ 1 \arrow[r, bend left=35] & a_2 / 1 \arrow[l, bend left=35] & a_2 / 0.8 \arrow[l]
    \end{tikzcd}\]
    % 
    Clearly $G$ has eight subgraphs, 
    then we get the following probability distribution over the subgraphs:
    % 
    \[
      \renewcommand{\arraystretch}{1.3} % 行距
      \renewcommand{\arraycolsep}{1.2em} % 列距
    \begin{array}{ccccccccc}
        \hline 
        & G_1 = G & G_2 & G_3 & G_4 & G_5 & G_6 & G_7 & G_8 \\ 
        
        I 
        & 0.8 & 0.2 & 0  \\
        \hline
    \end{array}
    \]
\end{example}




If all the arguments in a PrAF $G$ have probability of $1$, 
then the only subgraph of $G$ to have non-zero probability is itself, 
and so it has probability $1$. 
% 
At the other extreme,
if all the arguments in a probabilistic argument graph $G$ have probability of $0$, 
then the empty graph has probability $1$.








\vspace{3em}


Given a PrAF  $G = (Ar,\to,p)$, 
and a set of arguments $\Gamma \subseteq Ar$, 
we want to calculate the probability that $\Gamma$ is an $\sigma$--extension, 
which we denote by $P^\sigma_G(\Gamma)$,
where $\sigma \in \{ad, co, pr, gr, st\}$. 
For this, we take the sum of the probability of the full subgraphs for which $\Gamma$ is an $\sigma$--extension.



The analogous \textit{credulous acceptance problem} in the context of a probabilistic AF, 
i.e. the probability that a given set of arguments is an extension under a given semantics, is the following.


\[
    P_{PAF}^{\sigma,\circ} (a)
\]







\begin{df}[Probabilistic credulous acceptance]
    Given a PrAF $\mathcal{PF}=(Ar,\to,p)$, 
    an argument $a \in Ar$, 
    the probability $PrCA^\sigma_\mathcal{PF}(g)$ that $g$ is credulously acceptable w.r.t. semantics $\sigma$ is 
    \[
        PrCA^\sigma_\mathcal{PF}(g)
            = 
        \sum_{w \;\in\; pw(\mathcal{PF}) ~\land~ \exists E \;\in\; \sigma(w) ~s.t.~  g\; \in\; E} I(w).
    \]
\end{df}


The probability that an argument $g$ is credulously accepted according to a semantics $\sigma$ is defined as the sum of the probabilities of the possible worlds  of a PrAF for which argument $g$ is credulously accepted.





Computing $PrCA^\sigma_\mathcal{PF}(g)$ is $FP^{\#P}$--hard for all semantics $\sigma \in \{\mathcal{GR,PR,ST},\mathcal{STT}\}$ [Fazzinga, Flesca, and Furfaro 2018], 
where $FP^{\#P}$ is the class of functions computable by a polynomial-time Turing machine with a $\#P$ oracle.





Probabilistic credulous acceptance does not express the probability that a given argument is accepted. 
% 
However, 
a new problem, called \textit{Probabilistic Acceptance}, 
was given in \cite{Alf.Cal.Gre.Par.Tru2020} can be intuitively stated as follows.
% 
Given a probabilistic AF, 
a semantics $\sigma$ and a goal argument $g$, 
computing the probability that $g$ is accepted. 



\begin{df}[Probabilistic Acceptance]
    Given a PrAF $\mathcal{PF}=(Ar,\to,p)$ and an argument $g \in Ar$, 
    the probability $PrA^\sigma_\mathcal{AF}(g)$ that $g$ is acceptable w.r.t. semantics $\sigma$ is
    \[
        PrA^\sigma_\mathcal{AF}(g)
        =
        \sum_{w \in pw(\mathcal{PF}) \land E \in \sigma(w) \land g \in E} I(w) \cdot Pr(E,w,\sigma)
    \]
    where $Pr(\cdot,w,\sigma)$ is a $PDF$ over the set $\sigma(w)$.
\end{df}







\subsection{the shortcomings of Independence Assumption}


Whilst assuming independence brings some advantages, 
there are situations where it is not appropriate as it does not capture the uncertainty correctly. 
To illustrate this, 
we consider the following example.
























\vspace{3em}

\dotfill




epistemic approach to probabilistic argumen- tation [Thimm, 2012; Hunter and Thimm, 2014; Baroni et al., 2014; Hunter and Thimm, 2017].





% /////////////////////////////////////
\subsection{Other approaches in probabilistic argumentation}


combining the epistemic and the constellation approach

apply probabilistic techniques in order to learn argumentation frameworks from data

model changing beliefs in argumentation




